Report

### 2021-01-06 report.Rmd
Add richness analysis

```{r, cache = FALSE}
loadd(log_bm_net_group_f3y, model_log_bm_f3y,
  summary_log_bm_f3y, vif_log_bm_f3y)
#loadd(bm_net_group_median, bm_vs_net_trends)
```

@@

nmds <- metaMDS(com, k = 2, trymax = 100)

@@

```{r}
diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
  "#f7f7f7", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061")

par(mfrow = c(1, 2))
stressplot(nmds)
title("Stress plot")
bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= diverging_pal[findInterval(bm_slope_df$bm_slope, seq(-0.2,.2, length.out = length(diverging_pal)))],
   cex = findInterval(bm_slope_df$bm, seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
title("Color = ; Size of points = biomass")

>>>>

```{r, cache = FALSE}
loadd(log_bm_net_group_f3y, model_log_bm_f3y,
  summary_log_bm_f3y, vif_log_bm_f3y)
#loadd(bm_net_group_median, bm_vs_net_trends)
loadd(bm_net_group_f3y)
loadd(bm_net_group_f3y)
loadd(rich_vs_net_trends)

#compute_my_lm_vs_net_model(
      #.df = filter(my_bm_net_group, !is.na(protocol_type)),
      #var_to_group = "variable"
#)
```

@@

@@

```{r, cache = TRUE}
nmds <- metaMDS(com, k = 2, trymax = 100)
```

```{r, fig.width = 8}
diverging_pal <- c("#67001f", "#b2182b", "#d6604d", "#f4a582", "#fddbc7",
  "#f7f7f7", "#d1e5f0", "#92c5de", "#4393c3", "#2166ac", "#053061")

par(mfrow = c(1, 2))
stressplot(nmds)
title("Stress plot")
bluefunc <- colorRampPalette(c("lightyellow", "darkred"))
ordiplot(nmds,type="n")
orditorp(nmds,display="species",col="gray",air=0.01)
orditorp(nmds, display="sites",
  col= diverging_pal[findInterval(bm_slope_df$bm_slope, seq(-0.2,.2, length.out = length(diverging_pal)))],
   cex = findInterval(bm_slope_df$bm, seq(1, 4, 1))/2,
  air=0.01, pch = "+", labels = "+")
title("Color = ; Size of points = biomass")
```
